### 2025-05-07 chapters/4-substructure.tex
Completed problems and rough solutions

    % TODO
\makeprob{Constant-Cutoff Substructure at MLL}{constant-cutoff-mll}{
    Find the radiator for \glslink{constant-cutoff}{constant-cutoff-groomed} angularities at MLL.
    %
    Include running coupling effects and freeze the coupling at a non-perturbative scale \(\mu_\text{NP}\).
    %
    Write the associated MLL cumulative distribution and probability distribution in closed form.
}

    % TODO
\makeprob{Constant-Subtraction Substructure at MLL}{constant-subtraction-mll}{
    Find the radiator for \glslink{constant-subtraction}{constant-subtraction-groomed} angularities at MLL.
    %
    Include running coupling effects and freeze the coupling at a non-perturbative scale \(\mu_\text{NP}\).
    %
    Write the associated MLL cumulative distribution and probability distribution in closed form.
}

%\makeprob{\(\star\) Multiplicity of Groomed Subjets \(\star\)}{simple-groomed-multiplicity}{
%    Using the leading-logarithmic principles of the partonic cascade, find the multiplicity distribution of subjets of radius \rsub{} within a jet of radius \Rjet{} that is groomed using the constant-cutoff algorithm.

%    \texttt{(Hint:)}
%    %
%    You may wish to refer to the solution of \Prob{subjet-multiplicity}.
%}

>>>>

\iffalse
\makeprob{Multiple Emissions in Simple Groomed Jets}{groomed-multiple-emissions}{
    Repeat the analysis of \Prob{multiple-emissions} to show that corrections to additive observable distributions due to multiple emissions are qualitatively similar in both groomed and ungroomed jets.
    %
    In particular, for both the \glslink{constant-cutoff}{constant-cutoff-groomed} and \glslink{constant-subtraction}{constant-subtraction-groomed} grooming algorithms (which approximate the behavior of Soft Drop and \PIRANHA{} grooming algorithms),
}
\fi

\makeprob{Substructure at MLL in Simple Groomed Jets I: Cutoff}{groomed-mll-i}{
    Find the radiator for \glslink{constant-cutoff}{constant-cutoff-groomed} angularities at MLL.
    %
    Include running coupling effects and freeze the coupling at a non-perturbative scale \(\mu_\text{NP}\).
    %
    Write the associated MLL cumulative distribution and probability distribution.
}

\makeprob{Substructure at MLL in Simple Groomed Jets II: Subtraction}{groomed-mll-ii}{
    Find the radiator for \glslink{constant-subtraction}{constant-subtraction-groomed} angularities at MLL.
}
